Verifying Demonstrations

### 2018-11-20 paper/protest-model.tex

Our protocol relies on \emph{witnesses} to certify and associate the proof to the location by creating a \emph{proof share}.
A witness is only allowed to create one proof share per protester to avoid the risk of count inflation.
Note that a participant of a protest can take the role of a protester but also act as witness for other protesters.
The participation proof and its proof shares are stored as a set.
%, as there should only be unique proof shares.

@@

We will use the following notation to filter out a subset of \(\pshs\) with specific \(\cid\)s and \(\pid\)s:
\begin{multline*}
  \pshs_{\cid_0, \pid_0} = \\
  \{(\cid, t, l, \pid, \wid)\in \pshs\mid \cid = \cid_0 \land \pid = \pid_0\}.
\end{multline*}

A subset of the proof shares forms a participation proof for a protester.

@@

% strength
\NewFunction{\str}{\varsigma}

>>>>

Our protocol relies on \emph{witnesses} to certify and associate the proof to the location by creating a \emph{proof share}.
A witness is only allowed to create one proof share per protester to avoid the risk of count inflation.
(Note that a participant of a protest can take the role of a protester but also 
act as witness for other protesters.)
All the proof shares together form the participation proof.

@@

A subset of the proof shares forms a participation proof for a protester.
We will use the following notation to filter out a subset of \(\pshs\) with specific \(\cid\)s and \(\pid\)s:
\begin{multline*}
  \pshs_{\cid_0, \pid_0} = \\
  \{(\cid, t, l, \pid, \wid)\in \pshs\mid \cid = \cid_0 \land \pid = \pid_0\}.
\end{multline*}

@@

% strength
